\maketitle
\makesignature

\ifproject
\begin{abstractTH}
% เขียนบทคัดย่อของโครงงานที่นี่
    ปัจจุบันมหาวิทยาลัยเชียงใหม่มีการติดตั้งระบบโซลาร์เซลล์แล้วแต่ยังพบความไม่สอดคล้องระหว่างการใช้ไฟฟ้าและปริมาณการผลิตไฟฟ้าจากพลังงานแสงอาทิตย์ โครงการนี้จึงได้พัฒนาระบบพยากรณ์การผลิตไฟฟ้า โดยอาศัยสถานีตรวจวัดสภาพอากาศร่วมกับเทคนิค Machine Learning เพื่อให้ผู้ใช้สามารถวางแผนการจัดสรรการใช้ห้องเรียนและห้องประชุมให้สอดคล้องกับปริมาณไฟฟ้าที่ผลิตได้จริง ผลลัพธ์ที่ได้จะช่วยลดการพึ่งพาไฟฟ้าจาก กฟผ. อีกทั้งยังเป็นการลดการปล่อยก๊าซคาร์บอนไดออกไซน์ และลดภาระค่าใช้จ่ายด้านคาร์บอนเครดิตของมหาวิทยาลัย
\end{abstractTH}

\begin{abstract}
    While Chiang Mai University has implemented solar energy systems, there is still a significant mismatch between power demand and supply. This study introduces a predictive forecasting model that integrates real-time weather data with machine learning algorithms to optimize energy management. By aligning the scheduling of academic facilities with forecasted solar output, the university can minimize its dependence on the Provincial Electricity Authority (PEA), reduce its carbon footprint, and effectively manage expenditures associated with carbon credits.
\end{abstract}

\iffalse
\begin{dedication}
This document is dedicated to all Chiang Mai University students.

Dedication page is optional.
\end{dedication}
\fi % \iffalse

\begin{acknowledgments}
Your acknowledgments go here. Make sure it sits inside the
\texttt{acknowledgment} environment.

\acksign{2020}{5}{25}
\end{acknowledgments}%
\fi % \ifproject

\contentspage

\ifproject
\figurelistpage

\tablelistpage
\fi % \ifproject

% \abbrlist % this page is optional

% \symlist % this page is optional

% \preface % this section is optional
